\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2021-11-24 main.tex
Updates from Overleaf

@@

@@

% \subsection{Application: scanning SQUID magnetometry}
% \label{section:examples:magnetometry}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{examples/images/inductance.pdf}
    \caption{Self-inductance $L$ of a circular ring with inner radius $a$ and outer radius $b$ (see inset), as a function of the ratio $a / b$ and the ring's effective penetration depth $\Lambda$. Filled circles indicate results from \SuperScreen, solid lines show numerical results from Ref.~\cite{Brandt2004-ew} (Figure 2), blue squares and diamonds show numerical results from Ref.~\cite{Khapaev1997-kw} (Figure 1), and the dashed line indicates the analytical solution, $L = 2\mu_0 a$, for $\Lambda=0$ in the limit $a/b\to 0$\cite{Ketchen2012-mb, Babaei_Brojeny2003-la}. The \SuperScreen results were generated using a mesh with approximately 4,000 vertices and 8,000 triangles.}
    \label{fig:inductance}
\end{figure}

@@

The self-inductance $L$ of a 2D circular ring with inner radius $a$ and outer radius $b$ (see inset of Figure~\ref{fig:inductance}) has been used as an informal benchmark for superconducting inductance calculations. For a ring with effective penetration depth $\Lambda = 0$, it has been shown analytically that $L\to 2\mu_0 a$ in the limit $a/b\to 0$~\cite{Ketchen2012-mb, Babaei_Brojeny2003-la}. Khapaev calculated the inductance for $\Lambda = 0$ as a function of $a/b$~\cite{Khapaev1997-kw}, and Brandt and Clem calculated the inductance as a function of both $\Lambda$ and $a / b$~\cite{Brandt2004-ew}. Figure~\ref{fig:inductance} shows a comparison between these previous numerical results and the results from \SuperScreen. Note that the models used by Brandt and Clem (solid lines) and by the LCR2D software (blue diamonds) require a circularly symmetric film, whereas \SuperScreen (filled circles) and 3D-MLSI~\cite{Khapaev1997-kw, Khapaev2001-xq, Khapaev2001-pw} (blue squares) support arbitrary 2D geometry.

@@

\subsection{Application: scanning SQUID magnetometry}
\label{section:examples:magnetometry}

Scanning SQUID susceptometers can also be used for magnetometry, i.e. measuring the magnetic flux above a sample's surface without applying a field to the sample with the field coil.
